Output Summary

### 2022-04-05 03-post-process/output-plots.Rmd
Rename "growth" to "Delta_L_Pb_Mb" for consistency throughout

---
title: "Output Summary"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "size-based-surv"
    input: text
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
    input: checkbox
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
editor_options: 
  chunk_output_type: console
---

@@

# growth from summer to spring
# summer parr mean length
L1 = "Summer to Spring 'Growth Factor'"
L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
match = c("int_lgrowth", "slp_lgrowth", "sig_lgrowth", "rho_lgrowth", "^growth[")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

@@

  # extract posterior summaries of growth outcomes
  growth_mean = post_summ(post, sub_index("^growth[year,pop]", year = ts_yrs, pop = j))["mean",]
  growth_lwr = post_summ(post, sub_index("^growth[year,pop]", year = ts_yrs, pop = j))["2.5%",]
  growth_upr = post_summ(post, sub_index("^growth[year,pop]", year = ts_yrs, pop = j))["97.5%",]

@@

  # extract posteriors of coefficients
  int_lgrowth = post_subset(post, sub_index("int_lgrowth[pop]", pop = j), matrix = TRUE)
  slp_lgrowth = post_subset(post, sub_index("slp_lgrowth[pop]", pop = j), matrix = TRUE)

  # function to create predicted curves for one posterior sample
  pred_fn = function(i) {
    pred_growth = exp(int_lgrowth[i] + slp_lgrowth[i] * L_Pb_star_seq)
    names(pred_growth) = paste0("pred_growth[", 1:30, "1]")
    pred_growth
  }

  # calculate predicted growth values and add to posterior samples
  pred_growth = t(sapply(1:post_dim(post, "saved"), pred_fn))
  post_pred_growth = post_convert(cbind(postpack:::id_mat(post), pred_growth))

  # extract summarize predicted growth
  pred_growth_mean = post_summ(post_pred_growth, "")["mean",]
  pred_growth_lwr = post_summ(post_pred_growth, "")["2.5%",]
  pred_growth_upr = post_summ(post_pred_growth, "")["97.5%",]

  # make a blank plot with the correct dimensions
  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
  plot(1,1, type = "n", 
       ylim = range(pred_growth_lwr, pred_growth_upr, growth_lwr, growth_upr, na.rm = TRUE),
       xlim = range(L_Pb_seq), 
       main = pops[j]
  )

  # expected relationship
  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_growth_lwr, rev(pred_growth_upr)), border = NA, col = alpha("salmon", 0.5))
  lines(pred_growth_lwr ~ L_Pb_seq, col = "red", lty = 2)
  lines(pred_growth_upr ~ L_Pb_seq, col = "red", lty = 2)
  lines(pred_growth_mean ~ L_Pb_seq, col = "red", lwd = 2)

  # realized pairs
  segments(L_Pb_lwr, growth_mean, L_Pb_upr, growth_mean, col = alpha("red", 0.5))
  segments(L_Pb_mean, growth_lwr, L_Pb_mean, growth_upr, col = alpha("red", 0.5))
  points(growth_mean ~ L_Pb_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)

@@

  growth_obs = cbind(mean = jags_data$L_Mb_obs[observable,j]/jags_data$L_Pb_obs[observable,j],
                     lwr95 = NA, upr95 = NA)

  plot_tseries(post_summ(post, sub_index("^growth[year,pop]$", year = ts_yrs, pop = j)),
               growth_obs,
               main = pops[j],
               yrs = all_yrs[ts_yrs])
}

@@

# make prettier names for each term
rho_names = c(
  "rho_Lphi_E_Pb[2,1]" = "Egg-to-Parr Survival",
  "rho_lL_Pb[2,1]" = "Summer Mean Length",
  "rho_lgrowth[2,1]" = "Summer to Spring 'Growth Factor'",
  "rho_Lpi[2,1]" = "Mig. Strategy Apportionment",
  "rho_Lphi_Ma_O0[2,1]" = "LGR to Ocean Survival",
  "rho_Lphi_O0_O1[2,1]" = "Yr1 Ocean Survival",
  "rho_Lphi_Rb_Ra[2,1]" = "BON to LGR Survival",
  "rho_Lphi_Sb_Sa[2,1]" = "Pre-spawn Survival",
  "rho_Lphi_Pa_Mb[2,1,1]" = "Overwinter Survival (Fall)",
  "rho_Lphi_Pa_Mb[2,1,2]" = "Overwinter Survival (Spring)",
  "rho_Lphi_Mb_Ma[2,1,1]" = "Trib to LGR Survival (NOR)",
  "rho_Lphi_Mb_Ma[2,1,2]" = "Trib to LGR Survival (HOR)",
  "rho_Lpsi_O1[2,1,1]" = "Age-3 Maturation (NOR)",
  "rho_Lpsi_O1[2,1,2]" = "Age-3 Maturation (HOR)",
  "rho_Lpsi_O2[2,1,1]" = "Age-4 Maturation (NOR)",
  "rho_Lpsi_O2[2,1,2]" = "Age-4 Maturation (HOR)"
  )
rho_summs$name = rho_names[rho_summs$param]

@@

```{r growth-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("lgrowth_resid[year,pop]", "sig_lgrowth[pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "log(Summer to Spring Growth) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r proc-error-table-prep}
# rename parameters to human-readable format
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_E_Pb_resid\\[year,pop\\]", "Egg to Parr Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lL_Pb_resid\\[year,pop\\]", "Summer Parr Length")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpi_resid\\[year,pop\\]", "Migratory Strategy Apportionment")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Pa_Mb_resid\\[year,LH_type,pop\\]", "Overwinter Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lgrowth_resid\\[year,pop\\]", "Summer to Spring 'Growth Factor'")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Mb_Ma_resid\\[year,origin,pop\\]", "Trib to LGR Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Ma_O0_resid\\[year,origin\\]", "LGR to BON Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_O0_O1_resid\\[year,origin,pop\\]", "Yr1 Ocean Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpsi_O1_resid\\[year,origin,pop\\]", "Pr(Mature Age-3)")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpsi_O2_resid\\[year,origin,pop\\]", "Pr(Mature Age-4)")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Rb_Ra_resid\\[year,origin\\]", "BON to LGR Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Sb_Sa_resid\\[year,pop\\]", "Pre-spawn Survival")

>>>>

---
title: "Output Summary"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "size-based-surv-growth-relationship"
    input: text
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
    input: checkbox
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
editor_options: 
  chunk_output_type: console
---

@@

# growth from summer to spring
# summer parr mean length
L1 = "Summer to Spring 'Growth Factor'"
L2 = c("Intercept", "Slope", "Process SD", "Among-pop Correlation", "Realized")
match = c("theta0", "theta1", "sig_lDelta_L_Pb_Mb", "rho_lDelta_L_Pb_Mb", "^Delta_L_Pb_Mb[")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

@@

  # extract posterior summaries of growth outcomes
  Delta_L_Pb_Mb_mean = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["mean",]
  Delta_L_Pb_Mb_lwr = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["2.5%",]
  Delta_L_Pb_Mb_upr = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]", year = ts_yrs, pop = j))["97.5%",]

@@

  # extract posteriors of coefficients
  theta0 = post_subset(post, sub_index("theta0[pop]", pop = j), matrix = TRUE)
  theta1 = post_subset(post, sub_index("theta1[pop]", pop = j), matrix = TRUE)

  # function to create predicted curves for one posterior sample
  pred_fn = function(i) {
    pred_Delta_L_Pb_Mb = exp(theta0[i] + theta1[i] * L_Pb_star_seq)
    names(pred_Delta_L_Pb_Mb) = paste0("pred_Delta_L_Pb_Mb[", 1:30, "1]")
    pred_Delta_L_Pb_Mb
  }

  # calculate predicted growth values and add to posterior samples
  pred_Delta_L_Pb_Mb = t(sapply(1:post_dim(post, "saved"), pred_fn))
  post_pred_Delta_L_Pb_Mb = post_convert(cbind(postpack:::id_mat(post), pred_Delta_L_Pb_Mb))

  # extract summarize predicted growth
  pred_Delta_L_Pb_Mb_mean = post_summ(post_pred_Delta_L_Pb_Mb, "")["mean",]
  pred_Delta_L_Pb_Mb_lwr = post_summ(post_pred_Delta_L_Pb_Mb, "")["2.5%",]
  pred_Delta_L_Pb_Mb_upr = post_summ(post_pred_Delta_L_Pb_Mb, "")["97.5%",]

  # make a blank plot with the correct dimensions
  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
  plot(1,1, type = "n", 
       ylim = range(pred_Delta_L_Pb_Mb_lwr, pred_Delta_L_Pb_Mb_upr, Delta_L_Pb_Mb_lwr, Delta_L_Pb_Mb_upr, na.rm = TRUE),
       xlim = range(L_Pb_seq), 
       main = pops[j]
  )

  # expected relationship
  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_Delta_L_Pb_Mb_lwr, rev(pred_Delta_L_Pb_Mb_upr)), border = NA, col = alpha("salmon", 0.5))
  lines(pred_Delta_L_Pb_Mb_lwr ~ L_Pb_seq, col = "red", lty = 2)
  lines(pred_Delta_L_Pb_Mb_upr ~ L_Pb_seq, col = "red", lty = 2)
  lines(pred_Delta_L_Pb_Mb_mean ~ L_Pb_seq, col = "red", lwd = 2)

  # realized pairs
  segments(L_Pb_lwr, Delta_L_Pb_Mb_mean, L_Pb_upr, Delta_L_Pb_Mb_mean, col = alpha("red", 0.5))
  segments(L_Pb_mean, Delta_L_Pb_Mb_lwr, L_Pb_mean, Delta_L_Pb_Mb_upr, col = alpha("red", 0.5))
  points(Delta_L_Pb_Mb_mean ~ L_Pb_mean, pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)

@@

```{r}
plot_f = function(j) {
  Delta_L_Pb_Mb_obs = cbind(mean = jags_data$L_Mb_obs[observable,j]/jags_data$L_Pb_obs[observable,j], lwr95 = NA, upr95 = NA)
  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
               Delta_L_Pb_Mb_obs,
               main = pops[j],
               yrs = all_yrs[ts_yrs])
}

@@

# make prettier names for each term
rho_names = c(
  "rho_Lphi_E_Pb[2,1]" = "Egg-to-Parr Survival",
  "rho_lL_Pb[2,1]" = "Summer Mean Length",
  "rho_lDelta_L_Pb_Mb[2,1]" = "Summer to Spring 'Growth Factor'",
  "rho_Lpi[2,1]" = "Mig. Strategy Apportionment",
  "rho_Lphi_Ma_O0[2,1]" = "LGR to Ocean Survival",
  "rho_Lphi_O0_O1[2,1]" = "Yr1 Ocean Survival",
  "rho_Lphi_Rb_Ra[2,1]" = "BON to LGR Survival",
  "rho_Lphi_Sb_Sa[2,1]" = "Pre-spawn Survival",
  "rho_Lphi_Pa_Mb[2,1,1]" = "Overwinter Survival (Fall)",
  "rho_Lphi_Pa_Mb[2,1,2]" = "Overwinter Survival (Spring)",
  "rho_Lphi_Mb_Ma[2,1,1]" = "Trib to LGR Survival (NOR)",
  "rho_Lphi_Mb_Ma[2,1,2]" = "Trib to LGR Survival (HOR)",
  "rho_Lpsi_O1[2,1,1]" = "Age-3 Maturation (NOR)",
  "rho_Lpsi_O1[2,1,2]" = "Age-3 Maturation (HOR)",
  "rho_Lpsi_O2[2,1,1]" = "Age-4 Maturation (NOR)",
  "rho_Lpsi_O2[2,1,2]" = "Age-4 Maturation (HOR)"
  )
rho_summs$name = rho_names[rho_summs$param]

@@

```{r growth-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("lDelta_L_Pb_Mb_resid[year,pop]", "sig_lDelta_L_Pb_Mb[pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "log(Summer to Spring Growth Factor) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r proc-error-table-prep}
# rename parameters to human-readable format
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_E_Pb_resid\\[year,pop\\]", "Egg to Parr Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lL_Pb_resid\\[year,pop\\]", "Summer Parr Length")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpi_resid\\[year,pop\\]", "Migratory Strategy Apportionment")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Pa_Mb_resid\\[year,LH_type,pop\\]", "Overwinter Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lDelta_L_Pb_Mb_resid\\[year,pop\\]", "Summer to Spring 'Growth Factor'")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Mb_Ma_resid\\[year,origin,pop\\]", "Trib to LGR Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Ma_O0_resid\\[year,origin\\]", "LGR to BON Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_O0_O1_resid\\[year,origin,pop\\]", "Yr1 Ocean Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpsi_O1_resid\\[year,origin,pop\\]", "Pr(Mature Age-3)")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpsi_O2_resid\\[year,origin,pop\\]", "Pr(Mature Age-4)")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Rb_Ra_resid\\[year,origin\\]", "BON to LGR Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Sb_Sa_resid\\[year,pop\\]", "Pre-spawn Survival")
